MSDS 6371 Kaggle Project

### 2018-04-05 kaggle.Rmd
commit changes

library(xlsx)
source('code/01_LoadData.R')
# Creates dataframe:  hr_employee_attrition
```

@@

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

@@

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

source('code/01_LoadData.R')
# Creates dataframe:  hr_employee_attrition
```

@@

@@
